Election Security with Risk-Limiting Audits

### 2022-04-14 MultipleRoundSims/poster.tex
minor changes
full draft done except annoying bibtex error...

\usepackage{float}
\usepackage{xspace}
\usepackage{graphicx}
\graphicspath{{./imgs/}}
\usepackage{comment}
\usepackage{listings,hyperref}
\usepackage{cite}

@@

\begin{figure}[h]
\centering
\begin{minipage}{.49\textwidth}
\includegraphics[width=\textwidth]{bravo_risks.png}
\label{fig:bravo_risk}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[width=1.0\textwidth]{riskminerva1p5_10t4.png}
\label{fig:minerva_risk}
\end{minipage}
\caption{These plots show for $\chi_1=0.9$ the fraction of audits (EoR \BRAVO (left), SO \BRAVO (left), and \Minerva with multiplier $1.5$ (right)) that stopped in any of the $5$ rounds when the underlying election was a tie. (For SO \BRAVO audits we show the 13 states for which simulations are complete.)}
%\label{fig:risk}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{minipage}{.49\textwidth}
\includegraphics[width=1.0\textwidth]{eor_bravo_90perc_10^4_corrected/sprob_first_three_cropped.png}
\label{fig:eor_bravo_sprob}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[width=1.0\textwidth]{so_bravo_90perc_10^4/sprob_first_three.png}
\label{fig:so_bravo_sprob}
\end{minipage}
\caption{These plots show, for each state margin, when the underlying election is as announced, the number of audits that stopped in the $j^{th}$ round, as a fraction of all audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$ and $\chi_j=0.9$. The left shows EoR \BRAVO and the right shows SO \BRAVO.}
\end{figure}

\begin{figure}[h]
\centering
\begin{minipage}{.49\textwidth}
\includegraphics[width=1\textwidth]{minerva_multiround_1x_10^4/sprobs_first_three.png}
\label{fig:minerva1_sprob}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[width=1\textwidth]{minerva_multiround_1p5x_10^4/sprobs_first_three.png}
\label{fig:minerva1p5_sprob}
\end{minipage}
\caption{These plots show, for each state margin, when the underlying election is as announced, the number of \Minerva audits that stopped in the $j^{th}$ round, as a fraction of all \Minerva audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$. The left shows \Minerva with the round schedule obtained by $\chi_1=0.9$ and round size multiple $1.5$.}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{minerva25percthen1p5_sprob.png}
\caption{This plot shows, for each state margin, when the underlying election is as announced, the number of \Minerva audits that stopped in the $j^{th}$ round,
as a fraction of all \Minerva audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$, round size multiple of $1.5$ and $\chi_1 = 0.25$.}
\label{fig:minerva_25}
\end{centering}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{minipage}{.49\textwidth}
\includegraphics[width=1\textwidth]{texas25.png}
\label{fig:texas_25}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[width=1\textwidth]{missouri25.png}
\label{fig:missouri_25}
\end{minipage}
\caption{These plots show the cumulative fraction of audits that stopped as a function of average number of sampled ballots for all four audits we studied, for the states of Texas with margin $.057$ (left) and Missouri with margin $0.157$ (right), both with first round stopping probability $\chi_1=0.25$.}
\end{figure}

\begin{figure}[h]
\centering
\begin{minipage}{.49\textwidth}
\includegraphics[width=1\textwidth]{massachusetts25.png}
\label{fig:mass_25}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[width=1\textwidth]{texas90.png}
\label{fig:texas_90}
\end{minipage}
\caption{These plots show the cumulative fraction of audits that stopped as a function of average number of sampled ballots for all four audits we studied, for the states Massachusetts (left) with margin $0.342$ and $\chi_1=0.25$ and Texas (right) with margin $0.057$ and $\chi_1=0.9$.}
\end{figure}

@@

@@

\heading {Resistance against an adversary} 
If adversary $\mathcal{A}$ has knowledge of previous samples and chooses round size $n_j$ in round $j$, 
\Prov is still risk-limiting. Proof of this and the RLA property of \Prov are currently being revised for submission.

\heading {\Prov pilot}
In February 2022, The Rhode Island Board of Elections hosted a public pilot \Prov RLA which passed 
in the first round.

@@

@@

\footnotesize{\bibliographystyle{plain}\bibliography{audits}}

@@

\end{columns}

\end{frame}

\end{document}

>>>>

\usepackage{float}
\usepackage{xspace}
\usepackage{graphicx}
\graphicspath{{./imgs/}}
\usepackage{comment}
\usepackage{listings,hyperref}
\usepackage{cite}
\usepackage{hyperref}

@@

\begin{figure}[h]
\centering
\begin{minipage}{.49\textwidth}
\includegraphics[width=\textwidth]{bravo_risks.png}
\label{fig:bravo_risk}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[width=1.0\textwidth]{riskminerva1p5_10t4.png}
\label{fig:minerva_risk}
\end{minipage}
\caption{For $\chi_1=0.9$ the fraction of audits (EoR \BRAVO (left), SO \BRAVO (left), and \Minerva with multiplier $1.5$ (right)) that stopped in any of the $5$ rounds when the underlying election was a tie. (For SO \BRAVO audits we show the 13 states for which simulations are complete.)}
%\label{fig:risk}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{minipage}{.49\textwidth}
\includegraphics[width=1.0\textwidth]{eor_bravo_90perc_10^4_corrected/sprob_first_three_cropped.png}
\label{fig:eor_bravo_sprob}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[width=1.0\textwidth]{so_bravo_90perc_10^4/sprob_first_three.png}
\label{fig:so_bravo_sprob}
\end{minipage}
\caption{For each state margin, when the underlying election is as announced, the number of audits that stopped in the $j^{th}$ round, as a fraction of all audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$ and $\chi_j=0.9$. The left shows EoR \BRAVO and the right shows SO \BRAVO.}
\end{figure}

\begin{figure}[h]
\centering
\begin{minipage}{.49\textwidth}
\includegraphics[width=1\textwidth]{minerva_multiround_1x_10^4/sprobs_first_three.png}
\label{fig:minerva1_sprob}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[width=1\textwidth]{minerva_multiround_1p5x_10^4/sprobs_first_three.png}
\label{fig:minerva1p5_sprob}
\end{minipage}
\caption{When the underlying election is as announced, the number of \Minerva audits that stopped in the $j^{th}$ round, as a fraction of all \Minerva audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$. The left shows \Minerva with the round schedule obtained by $\chi_1=0.9$ and round size multiple $1.5$.}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{minerva25percthen1p5_sprob.png}
\caption{For each state margin, when the underlying election is as announced, the number of \Minerva audits that stopped in the $j^{th}$ round,
as a fraction of all \Minerva audits which had not yet stopped before the $j^{th}$ round for $j=1,2,3$, round size multiple of $1.5$ and $\chi_1 = 0.25$.}
\label{fig:minerva_25}
\end{centering}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{minipage}{.49\textwidth}
\includegraphics[width=1\textwidth]{texas25.png}
\label{fig:texas_25}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[width=1\textwidth]{missouri25.png}
\label{fig:missouri_25}
\end{minipage}
\caption{Cumulative fraction of audits that stopped as a function of average number of sampled ballots for all four audits we studied, for the states of Texas with margin $.057$ (left) and Missouri with margin $0.157$ (right), both with first round stopping probability $\chi_1=0.25$.}
\end{figure}

\begin{figure}[h]
\centering
\begin{minipage}{.49\textwidth}
\includegraphics[width=1\textwidth]{massachusetts25.png}
\label{fig:mass_25}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[width=1\textwidth]{texas90.png}
\label{fig:texas_90}
\end{minipage}
\caption{Cumulative fraction of audits that stopped as a function of average number of sampled ballots for all four audits we studied, for the states Massachusetts (left) with margin $0.342$ and $\chi_1=0.25$ and Texas (right) with margin $0.057$ and $\chi_1=0.9$.}
\end{figure}

@@

\heading {Resistance against an adversary} 
If for each round $j=1,2,\ldots$, 
adversary $\mathcal{A}$ has knowledge of all previous samples 
and is allowed to choose round size $n_{j+1}$ for round $j+1$, 
\Prov is still risk-limiting.

@@

\begin{block}{Providence Pilot}

In February 2022, The Rhode Island Board of Elections hosted a public pilot \Prov RLA which 
passed (met the risk limit) in the first round.

@@

\begin{figure}
\includegraphics[width=.65\textwidth]{prov_asn.png}
\caption{Cumulative fraction of audits that stopped as a function of average number of sampled ballots for the state of Texas with margin $.057$ with first round stopping probability $\chi_1=0.9$. \Prov, \Minerva with multiplier $1.5$, and both implementations of \BRAVO are included.}
\end{figure}

@@

%\footnotesize{
\bibliographystyle{plain}
\bibliography{audits}
%}

@@

\separatorcolumn
\end{columns}
\end{frame}
\end{document}
